### 2020-04-09 writeup/setup.tex
sec 3.1

\medskip
\noindent\textit{Jointly optimizing over both tasks.}
Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
\begin{align}
		&\val(\hat{B}; w_1, w_2) \nonumber\\
	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \\
	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}}
\end{align}

\todo{(multi-task training)}

\medskip
\noindent\textit{Optimizing over the target task.} The validation loss of using $w_2 \hat{B}(w)$ for the target task is
\begin{align}
	\val(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
\end{align}
In the above, the first is a bias term introduced by the model shift between the source and target tasks.
The second is a variance term, which decreases monotonically as we add more and more source task data.
Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
We will denote $\hat{\beta}_t^{\MTL} = w_2 \hat{B}(\hat{w})$.
\todo{(fine tuning)}
%\todo{may also consider test error}
%Several relevant directions on this setting.
%\begin{itemize}
%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
%\end{itemize}

>>>>

\medskip
\noindent\textit{Jointly optimizing over both tasks.}
Using a validation set that is sub-sampled from the original training dataset, we get a validation loss as follows
\begin{align}
		&\val(\hat{B}; w_1, w_2) \nonumber\\
	=& n_1 \cdot \bigbrace{\bignorm{\Sigma_1^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_2^{\top}X_2(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_1}} \nonumber \\
	+& n_2 \cdot \bigbrace{w^2\bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_s - w\beta_t)}^2 + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2}} \label{eq_val_mtl}
\end{align}
Minimizing the above loss is akin to performing multi-task training in practice.
Let $\hat{w}$ denote the minimizer of $\val(\hat{B}; w_1, w_2)$ over $w\in\real$.
We will denote $\hat{\beta}_t^{\MTL} = w_{2}\hat{B}(\hat{w})$.

\medskip
\noindent\textit{Optimizing over the target task.} The validation loss of using $w_2 \hat{B}(w)$ for the target task is
\begin{align}
	\val(w_2\hat{B}(w)) =&~ w^2 \bignorm{\Sigma_2^{1/2}(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - w \beta_t)}^2 \nonumber \\
			&~ + \sigma^2 \cdot \bigtr{(w^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2}. \label{eq_te_mtl}
\end{align}
In the above, the first is a bias term introduced by the model shift between the source and target tasks.
The second is a variance term, which decreases monotonically as we add more and more source task data.
Let $\hat{w}$ denote the minimizer of $te(w_2 \hat{B})$ over $w\in\real$.
Note that we can obtain the value of $\te(w_1\hat{B})$ through a validation set.
We will denote $\hat{\beta}_t^{\TL} = w_2 \hat{B}(\hat{w})$.

There are two reasons for studying this setting.
First, this is akin to performing transfer learning using the hard parameter sharing architecture.
Another way to obtain $\hat{\beta}_t^{\TL}$ is that once we minimize the multi-task validation loss, we further minimize the validation loss on the target dataset, which is also known as fine-tuning in practice.
%\todo{may also consider test error}
%Several relevant directions on this setting.
%\begin{itemize}
%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
%\end{itemize}
